Designing Types for R, Empirically

### 2020-05-15 paper/main.tex
minor
RW

In this section, we will introduce the R programming language, as well as
discuss the dynamic analysis framework we used as part of our initial
analysis.

%
%
\subsection{The R Programming Language}\label{sec:R}

>>>>

In this section, we will introduce related work and the R programming language.

\subsection{Related Work}

Dynamic programming languages such as Racket, JavaScript and PHP have been
extended post-facto with various static type systems.  In each case, the
type system was carefully engineered to match the salient characteristics of
the host languages and to foster a particular programming style. For
example, Typed Racket emphasizes functional programming and support the
migration from untyped to fully typed code~\cite{tf-popl08},
Hack~\cite{hack13} and TypeScript~\cite{BAT14} focus on typing
object-oriented features of PHP and JavaScript, respectively. They allow to
intersperse typed and untyped code in a fine-grained manner.

But what if the design of the type system is unclear?  \citet{tip} propose
an intriguing approach called trace typing. With trace typing, a new type
system can be prototyped and evaluated by applying the type rule to
execution traces of programs. While the appraoch has the limitation of
dynamic analysis techniques, namely that the results are only as good at the
coverage of the source code, it allows to quickly test new design and
quantify how much of a code base can be type-checked.  Other approaches that
infer types for dynamic analysis include the work of \citet{FurrAF2009} for
Ruby.

There is no previous work for the R programming language. We take
inspiration in the above mentionned works but focus on adapting them to our
target language.

%
\subsection{The R Programming Language}
